### 2014-11-25 stat343/hw7.tex
hw7 question 4 almost done

                \smallskip
                Estimated coefficients:
                \FloatBarrier
                \input{hw7/hw7_1_e} 
                \FloatBarrier
                \begin{center}
                    \includegraphics[width=9cm]{hw7/hw7_1_e} 
                \end{center}
        \end{itemize}
    \item[2.]
    \item[4.]
        As I think we had to show on the midterm,
        \begin{align*}
            H&= X(X^TX)^{-1}X^T //
            H&= QR(R^TQ^TQR)^{-1}R^TQ^T //
            H&= QR(R^TR)^{-1}R^TQ^T //
            H&= QRR^{-1}(R^T)^{-1}R^TQ^T //
            H&= QQ^T
        \end{align*}

>>>>

                \smallskip
                Estimated coefficients:
                \FloatBarrier
                \input{hw7/hw7_1_e} 
                \FloatBarrier
                \begin{center}
                    \includegraphics[width=9cm]{hw7/hw7_1_e} 
                \end{center}
        \end{itemize}
    \item[2.]
    \item[4.]
        As I think we had to show on the midterm,
        \begin{align*}
            H&= X(X^TX)^{-1}X^T \\
            H&= QR(R^TQ^TQR)^{-1}R^TQ^T \\
            H&= QR(R^TR)^{-1}R^TQ^T \\
            H&= QRR^{-1}(R^T)^{-1}R^TQ^T \\
            H&= QQ^T
        \end{align*}
        As was discussed with added variable plots, for an additional variable $X_i$ added to a regression, if $e_{(-i)}$ are the residuals from the regression excluding $X_i$ and $e$ are the residuals from the regression including it,
        \begin{align*}
            e_{(-i)} &= \hat\beta_i (I-H) X_i + e \\ 
            e_{(-i)} &= \hat\beta_i (I-QQ^T) X_i - e \\ 
        \end{align*}
        From simple linear regression, since \(e_{(-i)}\) has mean $0$, it must be the case that \(\hat\beta_i=\frac{\cov((I-QQ^T) X_i,e_{(-i)})}{\var((I-QQ^T) X_i)}\). Plugging this in, we get
        \begin{align*}
            e_{(-i)} &= \frac{\cov((I-QQ^T) X_i,e_{(-i)})}{\var((I-QQ^T) X_i)} (I-QQ^T) X_i - e \\ 
            e &= e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \\ 
            \|e\|^2 &= \left\|e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \right \|^2
            RSS &= \left\|e_{(-i)} - \frac{\cov\left((I-QQ^T) X_i,e_{(-i)}\right)}{\var\left((I-QQ^T) X_i\right)} (I-QQ^T) X_i \right \|^2
        \end{align*}
        Thus,
